Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-03 doc/PRF2022/PRF_main.tex
adding supplementary.tex
why these parameters?; Intro to section III;

The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
\infty$. The parameter $\rho_0$ is an ``effective" distance between
particle surfaces, below which the steric repulsion between a pair of
JPs becomes important. The parameter $M$ is the repulsion modulus.

@@

To perform a single time step, we first solve for the HAP by
solving~\eqref{eq:SL}--\eqref{eq:SLbc}, and then compute the force and
torque~\eqref{eq:FandTdef}. Then the Stokes
equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield} are solved, and
the force-free and torque-free conditions are used to compute the rigid
body motion~\eqref{eq:rigid-vel}.
Once~\eqref{eq:stokes}--\eqref{eq:force} have been solved, the
velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} update the
particle positions and orientations.  We use the parameters $\mu = 1$
mPa s, $\gamma = 4$ pN nm$^{-1}$, $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$
pN, and $\rho_0 = 0.5$ nm.  These values give a characteristic time $1$
ns and characteristic length $1$ nm.

@@

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
We consider boundary conditions of the form
\begin{align}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{align}
where $\alpha$ is the angle between the vector $\xx - \aa_i$ and 
the particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s =  1$.
The motivation for this normalization is that the hydrophobic attraction
part of the free energy converges to the integral of the square of the boundary
data in the zero-screening length limit.  
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

@@

>>>>

The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
\infty$. The parameter $\rho_0$ is an ``effective" repulsion distance between
particle surfaces, below which the steric repulsion between a pair of
JPs becomes important. The parameter $M$ is the repulsion modulus.

@@

To perform a single time step, we first solve for the HAP by
solving~\eqref{eq:SL}--\eqref{eq:SLbc}, and then compute the force and
torque~\eqref{eq:FandTdef}. Then the Stokes
equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield} are solved, and
the force-free and torque-free conditions are used to compute the rigid
body motion~\eqref{eq:rigid-vel}.
Once~\eqref{eq:stokes}--\eqref{eq:force} have been solved, the
velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} update the
particle positions and orientations.

@@

\section{Model parameters}
The interactions generated by the HAP-mobility problem formulation
\eqref{eq:stokes}--\eqref{eq:force}
lead to particle self-assembly for a broad range of parameters and
boundary conditions.  Generally speaking, the effective distance of the
hydrophobic interaction is set by the screening length $\rho$.
Smaller values of the repulsion distance $\rho_0$ decrease the distance
where attraction and repulsion are in balance and lead to more compact
particle assemblies. 
The rate of self assembly is proportional to the interfacial tension $\gamma$,
and inversely proportional to solvent viscosity $\mu$; it is
roughly inversely proportional to screening length $\rho.$

To give our system physical units, we set the model parameters
using phospholipids as a characteristic amphiphile in water \cite{Boal}.
For solvent viscosity, we use $\mu = 1$ mPa s for the viscosity
of water at room temperature.
Pure lipid components give a range
of interfacial tensions $0.7$ -- $5.3$ pN nm$^{-1}$
~\cite{KUZMIN2005, Petelska2012,Jackson2016,GarciaSaez}.
As in our previous works\cite{Fu20,Fu2022_JFM},
we use $\gamma=4.1$ pN nm$^{-1}$ since this value gave
good agreement with elastic moduli of lipid bilayers.
The particle radius $c = 1.25$ nm
gives a diameter representative of phospholipid length \cite{Boal},
and the screening length $\rho = 5$ nm
derives from experimental force-distance measurements of hydrophobic
attraction \cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}.
Based on empirical studies, the repulsion modulus $M = 2$ pN
and repulsion distance $\rho_0 = 0.5$ nm give an interparticle
distance around one particle radius.  This 
ensures the accuracy of the boundary integral representations
\eqref{eq:SL_BIE} and \eqref{eq:velocity}
without having to employ overly aggresive mesh refinement. 
Altogether, the above parameter set gives
a characteristic time $1$
ns and characteristic length $1$ nm.

\subsection{Boundary conditions and equilibrium configurations}
The boundary condition $g(\xx)$ in
\eqref{eq:SLbc} defines the spatial distribution of
hydrophobicity and hydrophilicity.  On a hydrophobic region of the
particle surface, representing a hydrocarbon-water interface,
for example, $g(\xx)$ takes relatively large values.
On an apolar, hydrophilic region, $g(\xx)$ is close to zero.

In the present work, we consider boundary conditions of the form
\begin{align}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{align}
where $\alpha$ is the angle between the vector $\xx - \aa_i$ and 
the particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s =  1$.
The motivation for this normalization is that the hydrophobic attraction
part of the free energy converges to the integral of the square of the boundary
data in the zero-screening length limit.  
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

@@

\input{Supplementary}
